Methodology for Assessing the State of the Practice for Domain X

### 2020-10-14 StateOfPractice/Methodology/Methodology.tex
updated commonality and variability in Section 7 of Methodology

The domain analysis consists of a commonality analysis of the family of software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. \cite{weiss1997defining} defines commonality analysis as an ``approach to defining a family by identifying commonalities, i.e., assumptions that are true for all family members, variabilities, i.e., assumptions about what can vary among family members, and common terminology for the family''.  The final result of the domain analysis will be tables of commonalities, variabilities, and parameters of variation of a program family, which \cite{parnas1976design} defines as ``a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members''. \cite{smith2008commonality} present a template for conducting a commonality analysis, which was referred to when conducting this work. \cite{weiss1998commonality} describes another commonality analysis technique for deciding the members of a program family which readers are encouraged to be familiar with. \cite{SmithAndChen2004} provide an example of a commonality analysis for mesh generating software. The steps to produce a commonality analysis are:

>>>>

The domain analysis consists of a commonality analysis of the family of software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. \cite{weiss1997defining} defines commonality analysis as an approach to defining a family by identifying commonalities, variabilities, and common terminology for the family. Commonalities are goals, theories, models, definitions and assumptions that are common between family members. Likewise, variabilities are goals, theories, models, definitions and assumptions that are different between family members. The final result of the domain analysis will be tables of commonalities, variabilities, and parameters of variation of a program family, which \cite{parnas1976design} defines as ``a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members''. \cite{smith2008commonality} present a template for conducting a commonality analysis, which was referred to when conducting this work. \cite{weiss1998commonality} describes another commonality analysis technique for deciding the members of a program family which readers are encouraged to be familiar with. \cite{SmithAndChen2004} provide an example of a commonality analysis for mesh generating software. The steps to produce a commonality analysis are:
